Guided Proofreading of Automatic Segmentations for Connectomics

### 2016-11-15 paper/results.tex
Results section complete.

\subsection{Automatic Error Correction}

\paragraph{Selection Oracle.} Accepting and rejecting proofreading corrections with the selection oracle yields the best performance on all datasets because all detected merge and split are corrected as long as the segmentation is improved. Fig.~\ref{fig:ac4trails} shows slope of VI reduction using the selection oracle on the AC4 subvolume. With focused proofreading, the selection oracle reaches a median VI of $0.353$ ($SD=0.037$) after $1605$ corrections. With guided proofreading, the oracle results in a median VI of $0.342$ ($SD=0.03$) after approximately $800$ corrections and then stagnates until all regions are proofread. Both results are very close to the best possible median VI of $0.334$ (calculated by computing maximum overlap with the ground truth). The slope of the trails in Fig.~\ref{fig:ac4trails} shows that guided proofreading requires less corrections to reach a reasonable reduction in VI. Fig.~\ref{fig:ac4boxplot} shows the VI distribution across methods.
The results on the L. Cylinder dataset (initial VI $XX$ ($SD=YY$) are similar: Focused proofreading reduces the median $VI$ to $XX$ ($SD=YY$) after 26,170 corrections. Guided proofreading reduces the median VI to $XX$ ($SD=YY$) after $XX$ corrections.

\paragraph{Automatic Method.}

\subsection{Merge vs. Split Error Detection}

\subsection{Limitations}

\begin{figure}[t]
\begin{center}
\includegraphics[width=\linewidth]{gfx/ac4boxplot.pdf}
\end{center}
  \vspace{-4mm}
   \caption{VI distributions of guided proofreading (GP), focused proofreading (FP) and Dojo output across the AC4 subvolume. The different decision approaches yield different proofreading performances. The performance of focused proofreading with automatic selection is an order of magnitude higher (as indicated by the arrow) and is reported in the text.}
\label{fig:ac4boxplot}
\end{figure}

>>>>

\begin{figure}[t]
\begin{center}
\includegraphics[width=\linewidth]{gfx/ac4boxplot.pdf}
\end{center}
  \vspace{-4mm}
   \caption{VI distributions of guided proofreading (GP), focused proofreading (FP) and Dojo output across the AC4 subvolume with different error correction approaches. The performance of focused proofreading with automatic selection is an order of magnitude higher (as indicated by the arrow) and is reported in the text.}
\label{fig:ac4boxplot}
\end{figure}
\subsection{Automatic Error Correction}

\paragraph{Selection oracle.} Accepting and rejecting proofreading corrections with the selection oracle yields the best performance on all datasets because all detected merge and split are corrected as long as the segmentation is improved. Fig.~\ref{fig:ac4trails} shows slope of VI reduction using the selection oracle on the AC4 subvolume (initial median VI $0.476$, $SD=0.089$). With focused proofreading, the selection oracle reaches a median VI of $0.353$ ($SD=0.037$) after $1605$ corrections. With guided proofreading, the oracle results in a median VI of $0.342$ ($SD=0.03$) after approximately $800$ corrections and then stagnates until all regions are proofread. Both results are very close to the best possible median VI of $0.334$ (calculated by computing maximum overlap with the ground truth). The slope of the trails in Fig.~\ref{fig:ac4trails} shows that guided proofreading requires less corrections to reach a reasonable reduction in VI. Fig.~\ref{fig:ac4boxplot} shows the VI distribution across methods.
The results on the L. Cylinder dataset (initial VI $0.379$, $SD=0.118$) are similar: Focused proofreading reduces the median VI to $0.298$ ($SD=0.075$) after $26,170$ corrections ($2,419$ accepted). Guided proofreading reduces the median VI to $0.2996$ ($SD=0.073$) after $27,491$ corrections ($2,696$ accepted).

\paragraph{Automatic selection with threshold.} Focused proofreading was not designed to run automatically. This explains very poor performance on the AC4 subvolume (VI of $1.9$, $SD=0.496$) and on the L. Cylinder dataset (VI of $2.75$, $SD=0.789$). For guided proofreading we define the threshold $p_t=0.95$ for both datasets. This reduces median VI in the AC4 subvolume to $0.398$ ($SD=0.068$). This is an impressive result and comparable to expert performance. Guided proofreading also reduces VI in the L. Cylinder data to $0.352$ ($SD=0.087$).

\paragraph{Merge Error Detection} Guided proofreading performs merge error detection prior to split error detection. The classifier automatically found 10 merge errors in the AC4 subvolume of which 4 reduce VI . Automatic selection with $p_t=0.95$ corrected all of these 4 true errors and in addition 2 false ones (precision/recall 0.67/1.00, f1-score 0.80). In 50 sections of the L. Cylinder dataset 151 merge errors were automatically found of which 17 reduce VI. Automatic selection with $p_t=0.95$ corrected 6 true errors and 30 false ones (precision/recall 0.17/0.35, f1-score 0.23). \DFH{Not good. The split error correction cleans up but still not good, might be bug. hard to track down on the large data.}

\subsection{Limitations}
Guided proofreading works on 2D image sections. This enables error correction without a computationally expensive alignment process. However, the output requires an additional (block-)merging step prior to 3D  analysis.
